### 2016-03-10 ch02-qlogms/excitation-design.tex
Remove line thingie in figure
Improve guideline 2.x
small changes ch-2,ch04

  We choose the resonance frequency of the systems such that
  \begin{equation}
   \wM\left( \wn \right)  = \omega_k + \beta \left( \omega_{k+1} - \omega_k \right)
   \text{ with } 0 \leq \beta < 1
   \label{eq:excitation:chosenVariationOmega}
  \end{equation}
  where $\omega_k$ and $\omega_{k+1}$ are the excited grid lines closest to the frequency $\wM$ where the FRF has its peak amplitude and $\beta$ is the misalignment coefficient that is varied over the interval $\RightOpenInterval{0,1}$ as depicted graphically in \figref{fig:excitation:misalignment-logms}
  This means that $\omega_k \leq \wM \leq \omega_{k+1}$ and that $\beta$ replaces the $\gamma$ factor in \eqref{eq:excitation:theoreticalBestVariationOmega}.
  If we take a look at the special case when $\beta=0$ (or $\beta=1$) in this expression, we see that this situation occurs when the peak value of the \gls{FRF} at $\wM$ coincides with the grid line $\omega_k$ or $\omega_{k+1}$ respectively.
  Intuitively, we study second order systems whose peak frequency $\wM$ is shifted between two neighboring excited frequency lines.
  From the previous section, we know that the exact frequency matters little as long as it remains within the bulk of the frequency grid.
  In this particular example $\wn$ was chosen at approximately $1 \unit{rad/s}$.

@@

  \begin{figure}[pht]
    \centering
    \remakeNextFigure
      \setlength\figurewidth{0.63\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/betaWC.tikz}
    \caption[Variance $\sigma_G^2\left( \wM \right)$ as a function of the grid misalignment coefficient $\beta$.]{Evaluation of the variance $\sigma_G^2\left( \wM \right) $ for different prototype systems as function of the misalignment $\beta$.
             The full lines depict the variance for a coarsely spaced signal.
             The dashed lines show the variance for a signal with the optimal $\alpha = \alpha^{\star}$ (see \eqref{eq:excitation:optimAlpha}).}
    \label{fig:excitation:worstCaseBeta}
  \end{figure}

@@

  \begin{figure}[pht]
    \centering
    \remakeNextFigure
      \setlength\figurewidth{0.63\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/alphaWC.tikz}
    \caption[Worst-case variance $\sigma_G^2\left( \wM \right)$ as a function of the frequency ratio $\alpha$.]{Worst case variance of the peak in the transfer function for logarithmic
             grid multisines and systems with different peak amplitudes.
             The dashed vertical line represents the optimal frequency spacing $\alpha^{\star}$.}
    \label{fig:excitation:worstCaseAlpha}
  \end{figure}

@@

  \begin{figure}[th]
    \centering
      \setlength\figurewidth{0.68\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/Sys02-4.tikz}
    \caption[Simulated \gls{FRF} and its variance for different excitation signals.]{\gls{FRF}~\legref{leg:excitation:sim:FRF} of a second order system with $\fR=40\unit{Hz}$ and $\damping=0.2$ along with the corresponding variance and bias of the parametric models obtained using three different kinds of multisine excitations.}%
    \label{fig:excitation:FRF1}
  \end{figure}

@@

  \begin{figure}%
    \centering
      \setlength\figurewidth{0.68\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/damping02-cmp.tikz}
    \caption[Simulated \glspl{FRF} and their variances of systems with $\damping=0.2$ for different excitation signals.]{%
       \Glspl{FRF} for different second order systems with constant damping $\damping=0.2$ but different resonance frequencies. 
       Comparison of the variance around the respective resonance frequency reveals the performance of each excitation signal.}%
    \label{fig:excitation:damping02}
  \end{figure}

@@

  \begin{figure}%
    \centering
      \setlength\figurewidth{0.68\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/damping005-cmp.tikz}
    \caption[Simulated \glspl{FRF} and their variances of systems with $\damping=0.05$ for different excitation signals.]{\Glspl{FRF} for different second order systems with constant damping $\damping=0.05$ but different resonance frequencies. 
    Comparison of the variance around the respective resonance frequency reveals the performance of each excitation signal.}%
    \label{fig:excitation:damping005}
  \end{figure}

@@

\begin{guideline}[Choose $2 \pi \Delta f \leq (\damping - \damping^2) \wn$]
\label{guide:excitation:systemInBulk:tuned}
 A quasi-logarithmic multisine with frequency resolution $\Delta f$ and tuned frequency spacing $\alpha=1+\damping$ is only guaranteed to properly excite resonances peaks with damping $\damping$ and resonance frequency $\wn$ when 
  \begin{equation}
    2 \pi \Delta f \leq (\damping - \damping^2) \wn 
    \approx \damping \wn \text{ if $\damping \ll 1$}
    \text{.}
    \label{eq:excitation:systemInBulk:tuned}
  \end{equation}
  \end{guideline}

@@

\begin{figure}%
  \centering
  \setlength\figurewidth{0.68\columnwidth}
  \setlength\figureheight{0.68\figurewidth}
  \input{\thisDir/figs/Sum02log0-2.tikz}
  \caption{FRF for the sum of two second order systems with $\damping=0.2$ and
           resonances at $ 400 \unit{Hz}$ and 4 \unit{kHz} as observed by a quasi-logarithmic multisine.}%
  \label{fig:excitation:sumSys}
\end{figure}

@@

    \begin{figure}%
    \centering
      \setlength\figurewidth{0.8\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/qlog_a050mall.tikz}
    \caption[Measured FRFs of all BK1613 octave filters and their variance for different excitation signals.]{Measured FRFs of the different \bruelkjaer BK1613 octave filters together with the observed variance for a linear, quasi-log and pink quasi-log grid multisine.}
      \label{fig:excitation:measurements}
    \end{figure}

>>>>

  We choose the resonance frequency of the systems such that
  \begin{equation}
   \wM\left( \wn \right)  = \omega_k + \beta \left( \omega_{k+1} - \omega_k \right)
   \text{ with } 0 \leq \beta < 1
   \label{eq:excitation:chosenVariationOmega}
  \end{equation}
  where $\omega_k$ and $\omega_{k+1}$ are the excited grid lines closest to the frequency $\wM$ where the FRF has its peak amplitude and $\beta$ is the misalignment coefficient that is varied over the interval $\RightOpenInterval{0,1}$ as depicted graphically in \figref{fig:excitation:misalignment-logms}.
  This means that $\omega_k \leq \wM \leq \omega_{k+1}$ and that $\beta$ has the same role as $\gamma$ factor in \eqref{eq:excitation:theoreticalBestVariationOmega}.
  If we take a look at the special case when $\beta=0$ (or $\beta=1$) in this expression, we see that this situation occurs when the peak value of the \gls{FRF} at $\wM$ coincides with the grid line $\omega_k$ or $\omega_{k+1}$ respectively.
  Intuitively, we study second order systems whose peak frequency $\wM$ is shifted between two neighboring excited frequency lines.
  From the previous section, we know that the exact frequency matters little as long as it remains within the bulk of the frequency grid.
  In this particular example $\wn$ was chosen at approximately $1 \unit{rad/s}$.

@@

  \begin{figure}[pht]
    \centering
      \setlength\figurewidth{0.63\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/betaWC.tikz}
    \caption[Variance $\sigma_G^2\left( \wM \right)$ as a function of the grid misalignment $\beta$.]{Evaluation of the variance $\sigma_G^2\left( \wM \right) $ for different prototype systems as function of the misalignment $\beta$.
             The full lines depict the variance for a coarsely spaced signal.
             The dashed lines show the variance for a signal with the optimal $\alpha = \alpha^{\star}$ (see \eqref{eq:excitation:optimAlpha}).}
    \label{fig:excitation:worstCaseBeta}
  \end{figure}

@@

  \begin{figure}[pht]
    \centering
      \setlength\figurewidth{0.63\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/alphaWC.tikz}
    \caption[Worst-case variance $\sigma_G^2\left( \wM \right)$ as a function of the frequency ratio $\alpha$.]{Worst case variance of the peak in the transfer function for logarithmic
             grid multisines and systems with different peak amplitudes.
             The dashed vertical line represents the optimal frequency spacing $\alpha^{\star}$.}
    \label{fig:excitation:worstCaseAlpha}
  \end{figure}

@@

  \begin{figure}[th]
    \centering
      \setlength\figurewidth{0.68\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/Sys02-4.tikz}
    \caption[Simulated \gls{FRF} of a single system using different excitation signals.]{\gls{FRF}~\legref{leg:excitation:sim:FRF} of a second order system with $\fR=40\unit{Hz}$ and $\damping=0.2$ along with the corresponding variance and bias of the parametric models obtained using three different kinds of multisine excitations.}%
    \label{fig:excitation:FRF1}
  \end{figure}

@@

  \begin{figure}%
    \centering
      \setlength\figurewidth{0.68\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/damping02-cmp.tikz}
    \caption[Simulated \glspl{FRF} of systems with damping $0.2$ for different excitation signals.]{%
       \Glspl{FRF} for different second order systems with constant damping $\damping=0.2$ but different resonance frequencies. 
       Comparison of the variance around the respective resonance frequency reveals the performance of each excitation signal.}%
    \label{fig:excitation:damping02}
  \end{figure}

@@

  \begin{figure}%
    \centering
      \setlength\figurewidth{0.68\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/damping005-cmp.tikz}
    \caption[Simulated \glspl{FRF} of systems with damping $0.05$ for different excitation signals.]{\Glspl{FRF} for different second order systems with constant damping $\damping=0.05$ but different resonance frequencies. 
    Comparison of the variance around the respective resonance frequency reveals the performance of each excitation signal.}%
    \label{fig:excitation:damping005}
  \end{figure}

@@

\begin{guideline}[Use a sufficient grid resolution for each resonance: $2 \pi \Delta f \leq (\damping - \damping^2) \wn$]
\label{guide:excitation:systemInBulk:tuned}
 A quasi-logarithmic multisine with frequency resolution $\Delta f$ and tuned frequency spacing $\alpha=1+\damping$ is only guaranteed to properly excite resonances peaks with damping $\damping$ and resonance frequency $\wn$ when 
  \begin{equation}
    2 \pi \Delta f \leq (\damping - \damping^2) \wn 
    \approx \damping \wn \text{ if $\damping \ll 1$}
    \text{.}
    \label{eq:excitation:systemInBulk:tuned}
  \end{equation}
  \end{guideline}

@@

\begin{figure}%
  \centering
  \setlength\figurewidth{0.68\columnwidth}
  \setlength\figureheight{0.68\figurewidth}
  \input{\thisDir/figs/Sum02log0-2.tikz}
  \caption[Simulated FRF of sum of two sub-systems.]{FRF for the sum of two second order systems with $\damping=0.2$ and            resonances at $ 400 \unit{Hz}$ and 4 \unit{kHz} as observed by a quasi-logarithmic multisine.}%
  \label{fig:excitation:sumSys}
\end{figure}

@@

    \begin{figure}%
    \centering
      \setlength\figurewidth{0.8\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/qlog_a050mall.tikz}
    \caption[Measurements of all BK1613 octave filters using different excitation signals.]{Measured FRFs of the different \bruelkjaer BK1613 octave filters together with the observed variance for a linear, quasi-log and pink quasi-log grid multisine.}
      \label{fig:excitation:measurements}
    \end{figure}
